Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-18 ehp_revision/response_to_reviewers.Rmd

\begin{shaded}
\textbf{R1 Comment 6:}
This is not a comment on the paper, but the authors may also want to consider
publishing their work in DesignSafe, which is "the web-based research platform
of the NHERI  [NSF-Funded Natural Hazards Engineering Research Infrastructure]
Network that provides the computational tools needed to manage, analyze, and
understand critical data for natural hazards research." It is the data
repository widely used by interdisciplinary hazards and disaster researchers.
\end{shaded}

**Response:**

It turns out that the data we present should already be accessible to use on the
DesignSafe platform, because we have shared the data as an R package.

DesignSafe is an online platform sponsored by the National Science Foundation as
part of the Natural Hazards Engineering Research Infrastructure
[@rathje2017designsafe]. This platform can be used to store, share, and publish
citable data related to natural hazards through its Data Depot. It goes beyond a
data repository, however, and also allows researchers to conduct data
integration and analysis in the cloud through its Discovery Workspace, while
drawing on data stored in the Data Depot and while using scientific programming
tools. As part of its platform, DesignSafe allows users to work in a number of
programming languages, including R (through Jupyter Notebooks)
[@rathje2017designsafe]. Therefore, DesignSafe users already have access to any
data shared through an R package, including the data we present in this
manuscript, without the data needing to be separately loaded and published
through DesignSafe's Data Depot.

@@

\begin{quotation}
\noindent
\textit{"For another set of tropical cyclones (e.g., Ernesto in 2006, and Bertha
in 1996, Isabel in 2003), there was moderate to good agreement for pairwise
combinations of distance, rain, and wind, but poor agreement for other
combinations of metrics, while for another set of storms (e.g., Matthew in 2004
and Katrina in 2005), there was moderate to good agreement between distance and
rain."}
\end{quotation}

\end{shaded}

**Response:**

We have included a measurement of agreement between different hazard-based
exposure metrics for two reasons. First, while we agree with the reviewer that a
direct measurement of each relevant hazard is preferable to a proxy, there are still some studies
that, when assessing tropical cyclone exposure based on measurements of physical
hazards, use a single hazard for this exposure assessment. We are most familiar
with cases where a wind-based metric has been the focus (e.g.,
@sun2020tropical, @grabich2015measuring). While this may not be 
ideal, it is done in practice. To interpret these studies, it is helpful to
understand the degree to which this single-hazard metric agrees with exposure
patterns for other hazards. If the exposure patterns are in strong agreement for
all hazards, then these studies could be interpreted as estimating risk
associated with exposure to tropical cyclones as a whole. If the exposure
patterns are in low to moderate agreement, then these studies should be
interpreted instead as estimating the risk associated with that specific storm
hazard, but not for all storm hazards. In this case, if the agreement is
moderate, there is a chance of confounding from other storm hazards
(i.e., an association that is attributed to one storm hazard was actually the
result of another that was not included in the model). In this paper, we present
measurements of agreement across four hazard-based exposure metrics that can
provide insights on these points.

@@

Second (and related), epidemiologists need to understand how these exposure
measurements agree to help in planning studies and statistical approaches to
interpreting the resulting data. In this sense, "agreement" is providing a
measure similar to correlation for continuous variables; our choice of agreement
with the binary exposure classifications reflects the more common use of binary
classifications for most tropical cyclone epidemiology to date.

There are several things that an epidemiologist could derive from these results
to help in designing a study and the associated statistical analysis. First, the
results we present can help epidemiologists determine if they can use a single
metric of tropical cyclone exposure in their studies, or if they need to instead
consider tropical cyclones as a mixture of hazards. There are a number of
practical reasons to use a single exposure metric, if doing so is reasonable
(even if it's not conceptually ideal). While there have been advances in methods
for mixtures research in environmental epidemiology, these are often more
complex than the long-used and well-developed methods for studying single
exposures, and many epidemiologists are much more comfortable with methods for
single exposures compared to methods for mixtures. Further, it can be easier to
communicate results from single-exposure studies clearly and succinctly.
Therefore, if there is a reasonable way to measure exposure with a single
metric, there are practical reasons that recommend that approach, even if
conceptually it might be preferable to incorporate separate hazards.

If, at the county level, there were strong agreement among exposure patterns for
the different tropical cyclone hazards we considered, it might have been
reasonable to recommend the use of a single hazard-based metric as a proxy for
exposure to all storm hazards in epidemiological studies for practical reasons.
We found that this is almost never the case, although there are a few select
storms (like Hurricane Floyd in 1999) where such an approach might be
justifiable. Most atmospheric scientists would not be surprised by our findings
about this disagreement in exposure patterns for different tropical cyclone
hazards, but this finding is not as self-evident for environmental
epidemiologists. Based on a recent conference of the International Society for
Environmental Epidemiology, for example, there are a number of environmental
epidemiologists with backgrounds focused on methods and other ambient exposures
(e.g., air pollution, heat) who are beginning to include tropical cyclones as an
exposure of interest in their studies, and we believe these results would be
novel and useful to many of them.

@@

\textit{Line 600--602 from original manuscript:}

\begin{quotation}
\noindent
\textit{"Based on our results, the use of a distance-based metric to assess
exposure to any of these hazards, or the use of measurements from one hazard as
a proxy for exposure to any of the other hazards considered, would often
introduce exposure misclassification."}
\end{quotation}
\end{shaded}

**Response:**

Figure 7 of the main text is meant to help illustrate the potential for exposure
misclassification, including when using a distance-based metric as a proxy. We
used the Jaccard index because we are using data for all eastern US counties.
For any storm, there will be large parts of this area that are
unquestionably unaffected, because they are so far from the storm. For example,
during Hurricane Floyd in 1999, the storm made landfall in North Carolina and
moved northward along the Eastern Seaboard. While there will be questions in
some case about whether counties in the Mid-Atlantic and New England were
exposed to this storm, counties in Texas, Louisiana, and other states in the
west of the study area were unquestionably unexposed to this storm. If we
measured misclassification using a metric that includes these counties in the
denominator, it would be overly optimistic because of the strong agreement in
counties far from the storm, like Texas counties during Hurricane Floyd, and
wouldn't help to pinpoint the potential for disagreement in areas nearer the
storm path.

We therefore used the Jaccard index, which focuses on counties that were
assessed as exposed based on at least one of the two metrics being compared.
However, one downside of this metric is that it does not help readers understand
the direction of that disagreement. For example, it does not provide information
about how many counties were classified as "exposed" based on a distance proxy
but "unexposed" by a hazard-based proxy. This could be useful in interpreting
our results in Figure 7 of the main table.

@@

\input{tables/rain_misclass.tex}

\input{tables/flood_misclass.tex}

\input{tables/tornado_misclass.tex}

We have added four new tables in the Supplemental Material (Tables S3--S6), one
for each of the hazard-based metrics we considered. We have reproduced these
tables at the end of this response document as Tables
\@ref(tab:misclasswind)--\@ref(tab:misclassflood). Each breaks down agreement
and disagreement between the distance-based proxy metric and one hazard-based
metric, focusing on storms with at least 200 counties exposed by at least one of
the metrics considered. These tables allow readers both to investigate general
patterns in disagreement and exposure misclassification across these storms and
also to see cases of unusual storms. For example, for most storms, disagreement
between the distance proxy metric and the wind-based metric resulted mainly from
mis-classification of counties as exposed based on distance while they did not
experience gale-force winds. However, there were a few storms, like Hurricane
Bertha in 1996, where the inverse was the case, and a distance-based metric
would have missed a large number of counties that experienced gale-force winds
from the storm (misclassified them as unexposed), but not misclassified many
counties as exposed when they in fact did not experience winds at this level.

@@

\textit{Lines 294--295 from original manuscript:}

\begin{quotation}
\noindent
\textit{"The tornado observations from this dataset form a traditional tornado
event database for the US, and so we did not further validate the tornado event
data."}
\end{quotation}
\end{shaded}

**Response:**

This database is NOAA's official database on tornado events in the United States
[@mccarthy2003nws]. It is the original source for the only other national
tornado database available for the country, the Storm Prediction Center [SPC]'s
National Tornado Database [@center2020storm], which provides a version of the
same data in which tornado events are joined into a single record in cases where
they cross county lines. There is no other comparable source of data on tornado
occurrences that could be used for a comparison as validation.

@@

\medskip

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

**Response:**

Ultimately, this choice will depend on what a researcher considers as plausible
causal pathways for the outcome he or she is studying. For example, if power
outages form a plausible step in the pathway, then the threshold for gale-force
or strong gale-force winds might be reasonable, while if the pathway is more
likely to be through larger-scale building destruction, a higher threshold would
be more reasonable.

For all outcomes, there are therefore various reasonable choices that can be picked for
the threshold in defining exposure. There is not room to go into these details
within Table 1, so instead we added a separate table to the Supplemental
Material that provides both some reasoning behind the thresholds selected in
this study and also other reasonable thresholds that could be considered.
This is Table S1 of the revised manuscript and has been reproduced as 
Table \@ref(tab:thresholds) at the end of this response document.

> **Text in the revised Methods (added text in bold)**:
"For other exposure metrics, each county was
classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table 1). We
picked reasonable thresholds (e.g., the threshold for gale-force wind for wind
exposure; **Table S1**), but others could be used with the open-source data and its
associated software."

@@

\medskip

\begin{shaded}
\textbf{EHP Request 2:}
Main text figures (general)
To ensure that figures are accessible to readers with impaired color vision, do not use color as the sole means of conveying information in a figure unless absolutely necessary. Use different symbols, shading/textures, and line patterns instead of (or in addition to) color to distinguish among different data points. Use contrasting colors that can be easily distinguished from each other when the figure is printed in black and white. For details, see: \url{https://ehp.niehs.nih.gov/authors/figures}.
\end{shaded}

**Response:**

In all these figures, we have used colormaps that are both accessible to readers
with several forms of color vision deficiency, including the most common type
(deuteranomaly, a type of red-green color vision deficiency), and can be easily
distinguished when the figure is printed in black and white [@viridis;
@van2015mpl]. The colormaps we used are all multi-hue sequential maps that avoid
red-green contrasts, while maximizing dynamic range in comparison to something
single-hued, like grayscale [@nunez2018optimizing; @viridis]. They are all
perceptually uniform across the scale for those with normal color vision
[@liu2018somewhere] and are close to perceptually uniform for those with common
forms of color deficiency [@nunez2018optimizing]. They reproduce their original
sequential gradient when printed in grayscale and so are perceptible when
printed on a black-and-white printer [@van2015mpl; @nunez2018optimizing].
Previous research has found that colormaps in this family allow viewers to more
quickly and accurately judge relative distances in scientific figures
[@liu2018somewhere]. The family of colormaps we used in the figures is currently
considered the gold standard for scientific figures [@nunez2018optimizing].

### 2020-09-19 ehp_revision/response_to_reviewers.Rmd

\input{tables/precip_high_corr.tex}

In several cases, the correlation was much weaker when limiting analysis to
these severe rainfall events. For example, in Miami-Dade County, FL, the
Spearman correlation coefficient was 0.94 for all 64 tropical cyclones that came
near the county over the analysis period, while it was only 0.49 among the 18
storms with cumulative precipitation of 75 mm or more. There was a similar
reduction in Mobile County, AL. However, for some counties, the correlation
remained high (e.g., Harris County, TX; Orleans Parish, LA), although in all
cases there are few extreme precipitation events (5--20 across
these sample counties), and so there is likely substantial random variation in
these correlation estimates, since they are based on small numbers of 
observations.

We have added text to mention this point and to direct readers to the added
supplemental table:

> **Text in revised Results (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2). **Further, in some counties, the correlation was substantially lower when 
considering only tropical cyclones with cumulative local rainfall of $\ge75$ mm
(Supplemental Table 2)**."

> **Text in revised Discussion (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based observations,
but may sometimes underestimate very high rainfall values (Figure 2), **and in
some counties the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of $\ge75$ mm (Supplemental
Table 2).**"

@@

\input{tables/tornado_misclass.tex}

We have added four new tables in the Supplemental Material (Tables S3--S6), one
for each of the hazard-based metrics we considered. We have reproduced these
tables at the end of this response document as Tables
\@ref(tab:misclasswind)--\@ref(tab:misclassflood). Each breaks down agreement
and disagreement between the distance-based proxy metric and one hazard-based
metric, focusing on storms with at least 200 counties exposed by at least one of
the metrics considered. These tables allow readers both to investigate general
patterns in disagreement and exposure misclassification across these storms and
also to see cases of unusual storms. For example, for most storms, disagreement
between the distance proxy metric and the wind-based metric resulted mainly from
mis-classification of counties as exposed based on distance while they did not
experience gale-force winds. However, there were a few storms, like Hurricane
Bertha in 1996, where the inverse was the case, and a distance-based metric
would have missed a large number of counties that experienced gale-force winds
from the storm (misclassified them as unexposed), but not misclassified many
counties as exposed when they in fact did not experience winds at this level.

We have added a reference to these new tables in the main text of the manuscript:

> **Text in the revised manuscript (relevant addition in bold):** 
"We drew similar conclusions when we investigated all 46 tropical cyclones
between 1996 and 2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric (Figure7;
**for the most extensive of these, storms for which 200 of more counties were
exposed based on at least one metric, Tables S3--S6 provide underlying numbers
comparing exposure assessments between the distance-based proxy and each
hazard-based metric**)."

@@

\begin{shaded}
\textbf{Reviewer 3 (R3) Comment 1:}
Starting on line 128, the authors write "Extreme winds are more common to the
track's right, where counterclockwise cyclonic winds move in concert with the
tropical cyclone's forward motion". I think this statement may be specific to
tropical cyclones in the Northern hemisphere (i.e., those relevant to exposure
in the US). Would be good to clarify this.
\end{shaded}

**Response:**

You are right, the opposite would be true in the Southern hemisphere. This
difference is driven by the Coriolis effect on cyclonic rotation, in which the
rotation of the earth diverts winds as they move toward the low pressure center
of the cyclone. We have edited the text to specify that this statement is
specific to the Northern Hemisphere:

> **Text in revised manuscript (relevant addition in bold):**
"**In the Northern Hemisphere, cyclonic winds are counterclockwise,** so
extreme winds are more common to the track's right where cyclonic winds move in
concert with the tropical cyclone's forward motion (Halverson 2015)."

@@

\textbf{Rain} & Rain-based exposure was determined based on whether the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. One recent study has highlighted that a two-year rainfall value (which is the median annual maximum rainfall) for a location can provide a useful threshold in identifying rainfall events with potential for societal impacts [@bosma2020intuitive]. For some of the more northern, inland communities included in our study area, the two-year rainfall value for two-, three- and four-day windows is in the 65--85 mm range. For example, Pittsburgh, PA, has two-year rainfall values of 69 mm for a two-day window, 74 mm for a three-day window, and 78 mm for a four-day window [@noaaatlas], consistent with the 75 mm threshold we selected for exposure classification in this paper. However, other thresholds, particularly higher thresholds, would be reasonable in some cases. For example, the two-year rainfall values tend to be much higher in counties of the study area that are further south and close to the coast. The two-year rainfall value for Miami for a three-day window, for example is 180 mm [@noaaatlas]. A variety of definitions have been used previously to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall [@zhou2017spatial] and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---\parfillskip=0pt\tabularnewline

&in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location [@feldmann2019estimation]. Other definitions of extreme rain events---including but not limited to tropical cyclone--associated rainfall---are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours [@schumacher2006characteristics]. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]) [@schumacher2006characteristics; @schumacher2005organization; @stevenson201410].\\

\textbf{Wind} & Wind-based exposure was determined based on whether modeled storm-associated peak sustained surface wind was $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts [@cangialosi2016examination]. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those, only for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

### 2020-09-19 ehp_revision/tables/thresholds_table.tex
Work some more on revisions

&in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location \parencite{feldmann2019estimation}. Other definitions of extreme rain events---including but not limited to tropical cyclone--associated rainfall---are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours \parencite{schumacher2006characteristics}. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]). \parencite{schumacher2006characteristics, schumacher2005organization, stevenson201410}.\\

\textbf{Wind} & Wind-based exposure was determined based on whether modeled storm-associated peak sustained surface wind were $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts \parencite{cangialosi2016examination}. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

>>>>

&in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location \parencite{feldmann2019estimation}. Other definitions of extreme rain events---including but not limited to tropical cyclone--associated rainfall---are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours \parencite{schumacher2006characteristics}. Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]) \parencite{schumacher2006characteristics, schumacher2005organization, stevenson201410}.\\

\textbf{Wind} & Wind-based exposure was determined based on whether modeled storm-associated peak sustained surface wind was $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts \parencite{cangialosi2016examination}. Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those, only for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

### 2020-09-19 ehp_revision/writing/ehp_discussion.tex
Work some more on revisions

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}), \textbf{and in some counties the
correlation was substantially lower when considering only tropical cyclones
with cumulative local rainfall of $\ge75$ mm (Supplemental Table 1).} When
rainfall data is used to create binary exposure classifications, this
disagreement is unlikely to influence results, as both data sources agree in
identifying these as storms with high rainfall, but would be important to
consider for cases that include rainfall as a continuous measurement.

>>>>

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}), \textbf{and in some counties the
correlation was substantially lower when considering only tropical cyclones
with cumulative local rainfall of $\ge75$ mm (Supplemental Table 2).} When
rainfall data is used to create binary exposure classifications, this
disagreement is unlikely to influence results, as both data sources agree in
identifying these as storms with high rainfall, but would be important to
consider for cases that include rainfall as a continuous measurement.

### 2020-09-19 ehp_revision/writing/ehp_introduction.tex
Work more on response
Work some more on revisions

Further, when studies use distance from the storm's track to assess exposure,
they often use the same buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  \textbf{In
the Northern Hemisphere,} extreme winds are more common to the track's right,
where counterclockwise cyclonic winds move in concert with the tropical
cyclone's forward motion~\parencite{halverson2015}, and almost all of the fatal
tornadoes associated with \ac{US} tropical cyclones between~1995 and~2009
occurred to the right of the tropical cyclone's track~\parencite{moore2012}.
Rain, conversely, is often heaviest to the left of the track, especially when
the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

>>>>

Further, when studies use distance from the storm's track to assess exposure,
they often use the same buffer constraints on each side of the storm track
(e.g.,~\cite{kinney2008, currie2013}).  However, the forces of a tropical
cyclone tend to be distributed around its center non-symmetrically.  \textbf{In
the Northern Hemisphere, cyclonic winds are counterclockwise,} so extreme winds
are more common to the track's right where cyclonic winds move in concert with
the tropical cyclone's forward motion~\parencite{halverson2015}, and almost all
of the fatal tornadoes associated with \ac{US} tropical cyclones between~1995
and~2009 occurred to the right of the tropical cyclone's
track~\parencite{moore2012}.  Rain, conversely, is often heaviest to the left
of the track, especially when the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

### 2020-09-19 ehp_revision/writing/ehp_results.tex
Work some more on revisions

We explored potential limitations in these data by comparing them with data
from other available sources.  For estimates of storm-associated rainfall, we
compared data in the open-source package with ground-based observations in nine
sample counties (Figure~\ref{fig:raincomparison}). Within these counties,
storm-related rainfall measurements were well-correlated between the two data
sources, with rank correlations (bottom right of each graph in
Figure~\ref{fig:raincomparison}) between 0.87 and 0.98.  There was some
evidence that our primary rainfall metric may tend to underestimate rainfall
totals in storms with extremely high rainfall, based on a few heavy-rainfall
storms in Harris County, TX, Mobile County, AL, Charleston County, SC, and Wake
County, NC (Figure~\ref{fig:raincomparison}). \textbf{Further, in some
counties, the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of $\ge75$ mm (Supplemental
Table 1).} However, even in these cases, it was rare for a storm to be
classified differently (under the precipitation threshold of
75~\si{\milli\metre} we used for binary exposure classification for later
analysis) based on the source of precipitation data. Horizontal and vertical
lines in each small plot in Figure~\ref{fig:raincomparison} show the threshold
of 75~\si{\milli\metre}, so storms in the lower left and upper right quadrants
would be classified the same (``exposed'' or ``unexposed'') regardless of the
precipitation data source, while storms in the upper left and lower right
quadrants would be classified differently. Such cases were rare.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}; \textbf{for the most extensive of these, storms for
which 250 of more counties were exposed based on at least one metric, Tables
S3--S6 provide underlying numbers comparing exposure assessments for the
distance-based proxy to each hazard-based metric}). In \textbf{Figure 7}, each row
provides results for one tropical cyclone, and each box in that row shows the
Jaccard coefficient for a pair of metrics. For all pairs of metrics, agreement
in exposure assessment was, at best, moderate for all but a few storms. When
comparing distance- and wind-based exposure assessment, only about 10\% of
storms had Jaccard indices higher than 0.6 (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
more were assessed the same under both metrics). For comparisons of assessments
based on other combinations of distance-, wind-, rain-, and flood-based
metrics, fewer than 5\% of storms had Jaccard indices above 0.6.  The
tornado-based metric had universally poor agreement with other metrics in
county-level classification across the tropical cyclones considered.

>>>>

We explored potential limitations in these data by comparing them with data
from other available sources.  For estimates of storm-associated rainfall, we
compared data in the open-source package with ground-based observations in nine
sample counties (Figure~\ref{fig:raincomparison}). Within these counties,
storm-related rainfall measurements were well-correlated between the two data
sources, with rank correlations (bottom right of each graph in
Figure~\ref{fig:raincomparison}) between 0.87 and 0.98.  There was some
evidence that our primary rainfall metric may tend to underestimate rainfall
totals in storms with extremely high rainfall, based on a few heavy-rainfall
storms in Harris County, TX, Mobile County, AL, Charleston County, SC, and Wake
County, NC (Figure~\ref{fig:raincomparison}). \textbf{Further, in some
counties, the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of $\ge75$ mm (Supplemental
Table 2).} However, it was rare for a storm to be classified differently (under
the precipitation threshold of 75~\si{\milli\metre} we used for binary exposure
classification for later analysis) based on the source of precipitation data.
Horizontal and vertical lines in each small plot in
Figure~\ref{fig:raincomparison} show the threshold of 75~\si{\milli\metre}, so
storms in the lower left and upper right quadrants would be classified the same
(``exposed'' or ``unexposed'') regardless of the precipitation data source,
while storms in the upper left and lower right quadrants would be classified
differently. Such cases were rare.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}; \textbf{for the most extensive of these, storms for
which 200 of more counties were exposed based on at least one metric, Tables
S3--S6 provide underlying numbers comparing exposure assessments between the
distance-based proxy and each hazard-based metric}). In \textbf{Figure 7}, each row
provides results for one tropical cyclone, and each box in that row shows the
Jaccard coefficient for a pair of metrics. For all pairs of metrics, agreement
in exposure assessment was, at best, moderate for all but a few storms. When
comparing distance- and wind-based exposure assessment, only about 10\% of
storms had Jaccard indices higher than 0.6 (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
more were assessed the same under both metrics). For comparisons of assessments
based on other combinations of distance-, wind-, rain-, and flood-based
metrics, fewer than 5\% of storms had Jaccard indices above 0.6.  The
tornado-based metric had universally poor agreement with other metrics in
county-level classification across the tropical cyclones considered.
